---
title: "Homework 5"
author: Akanksha Nalatwad
output: html_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicide_df=
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state= str_c(city, state, sep = "_"),
    resolved= case_when(
      disposition=="Closed without arrest"~ "unsolved",
      disposition=="Open/No arrest"       ~ "unsolved",
      disposition== "Closed by arrest"      ~"solved"
      )
  ) %>% 
  select(city_state,resolved) %>% 
  filter(city_state !="Tulsa_AL")
```
Let's look at this a bit

```{r}
aggregate_df=
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total=n(),
    hom_unsolved= sum(resolved=="unsolved")
  )
  
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter (city_state=="Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter (city_state=="Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

 
Try to iterate.....

```{r}
results_df=
aggregate_df %>% 
  mutate(
    prop_tests= map2(.x=hom_unsolved, .y=hom_total, ~prop.test(x=.x, n=.y)),
    tidy_tests= map (.x= prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state=fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x=city_state, y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high))+
  theme(axis.text.x= element_text (angle=90, vjust=0.5, hjust=1))
```
## Problem 2

Data Mapping and Tidying


```{r}
path_df=
tibble(
  path= list.files("lda_data")
) %>% 
  mutate(path=str_c("lda_data/", path),
         path_2=path,
         data=map(path, read_csv)) %>% 
  separate(col=path_2, into=c("path_a", "path_b"), sep=9, remove=T) %>% 
  separate(col=path_b, into= c("arm", "id_number", sep=3)) %>% 
  select(-path_a,-c(5)) %>% 
  mutate(
  arm=str_replace(arm,"exp","Experimental"), 
  arm=str_replace(arm, "con", "Control")) %>% 
  within(Arm_ID <- paste(arm, id_number, sep='_')) %>% 
  select(-id_number) %>% 
  unnest(data) %>%
 pivot_longer(week_1:week_8,
              names_to="week_number",
              values_to="weekly_observation"
            ) %>% 
  mutate(
    week_number= str_replace(week_number, "week_", "")
  )
```

## Spaghetti Plot
```{r}
plot_p=
ggplot(data = path_df, aes(x = week_number, y = weekly_observation, group = Arm_ID))+
   geom_line(aes(linetype=arm))
```
Comments on Plot:

It looks like generally the experimental patients had higher weekly observations than the control patients. In general, experimental patients showed less dramatic differences in observations by week compared to control patients. Additionally, it looks like the experimental patients' observations increased over time compared to control patients who fluctuated around the same number of observations. 

## Problem 3

Function

```{r, cache=TRUE}

library(broom)
n=30
sigma=5
mu=c(0,1,2,3,4,5,6)
mean=mu
sd=sigma

sample = function(n, mean, sd){
samp_data = tibble(
samp = rnorm(n, mean, sd)
)

samp_result = nest(samp_data) %>%
mutate(
  t_test = map(.x = data, ~{tidy(t.test(x = .x,mu=0, alternative = 'two.sided', paired = FALSE, conf.level = 0.95))})) %>% 
unnest(t_test)

return(samp_result)
}

```

```{r}
mean_list =
  list(
    "mean_0" = 0,
    "mean_1" = 1,
    "mean_2" = 2,
    "mean_3" = 3,
    "mean_4" = 4,
    "mean_5" = 5,
    "mean_6" = 6
    )

output = vector("list", length = 7)

for (i in 1:7) {
  output[[i]] = rerun(10, sample(10, mean_list[[i]], 5)) %>% 
  bind_rows()
}

sim_results = 
  tibble(mu = c(0,1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x =mu, ~rerun(10, sample(10, mean_list[[i]], 5))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  select(mu,p.value, estimate) %>% 
  mutate(
    hyp_test=ifelse(p.value > 0.05, "fail_to_reject", "reject")
  )

```

## Plot 1: Effect Size and Power

```{r}

```


## Plot 2: True Mu vs Estimated Mu

## Plot3: True Mu vs Estimated Mu, Only in Examples For Which Null Was Rejected


